Vulnerability Analysis of Container Images in Neuroimaging

### 2020-05-21 paper.tex
revised content

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

\textbf{not-affected:} The package (inside the given release), while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information if needed. For e.g
		"not-affected (1.14.6-1.1)" indicates that this specific
		package version in the given release is not affected.

@@

\textbf{ignored:} The package (inside the given release), while related to the
		CVE in some way, is being ignored for some reason.  The
		notes should provide that reason. For e.g "ignored (reached end-of-life)".
		This means that this given Ubuntu release already reached
		end-of-life so this CVE is ignored by Ubuntu. However, if there
		is extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package (inside the given release) is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The "version" indicates the package version 
		  that contains the fix.

@@

\textbf{released-esm:} The package (inside the given release) was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by
		+esmN or ~esmN, indicating that this package version is available
		only via ESM.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\subsection{Image size Reduction process}
If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
a list of unnecessary packages.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities and lastly, this section presents the effect of image size reduction on the
vulnerabilities.

@@

Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

@@

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a Linux-Kernel header packages, referring to different databases,
how frequently they are updating their databases, etc.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.
Linux-kernel-headers are the headers files that only provide function names, its parameters, and its
return type.
The actual source code of these functions is present in the Linux kernel and not inside the image.
So, vulnerability detection in header files
is irrelevant in this case.

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
as "not-affected". So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
is not affected by this CVE.

\textbf{With CVE status as "Ignored (reached end-of-life)":}
Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
release so Clair Scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images still
Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.

@@

\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
		detected by Anchore due to the presence of epoch in the Procps package version.

\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

\textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}
\subsection{Effect Of Update}
\begin{comment}
The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
\end{comment}

When the images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
\begin{comment}
There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images.
After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
Also, after the update, the number of vulnerabilities have a mild slope meaning that there
are a fixed set of packages that contain vulnerabilities and have no fix yet.
%\begin{figure*}[h]
%        {\includegraphics[width=\textwidth]
%        {Figures/vulnwithupdate.pdf}}
%        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
%	after update of the images}
%      \end{figure*}

@@

Our third experiment shows deleting unnecessary packages from the image also helps to reduce
the number of vulnerabilities by a significant number. We started this experiment with
\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Our initial thought was that it will reduce the number of vulnerabilities significantly. Howver
we analyzed that this is not always true. It depends on which packages you are deleting and how
many vulnerabilities they contain. In particular, if a package contains a large number of vulnerabilities
it means deleting that package will help to reduce vulnerabilities in that image by a significant number.
Contrary

@@

None of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some are critical vulnerabilities. Yet there is not a single image scanner on which we can reply upon for
scanning. Additionally, we cannot update all images because some OS already reached end-of-life and are
no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
the pipeline to get Reprozip trace that can take upto several hours. Also user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Also there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
branch of the program. So there should be some kind of coverage measurement.

>>>>

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
distribution can have different releases. As images in our experiments mostly have
Ubuntu distribution we can take this distribution as an example. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

\textbf{not-affected:} The package (inside the given release), while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information if needed. For e.g if the given
		status is "not-affected (1.14.6-1.1)" then it indicates that this specific
		package version in the given release is not affected.

@@

\textbf{ignored:} The package (inside the given release), while related to the
		CVE in some way, is being ignored for some reason.  The
		notes should provide that reason. For e.g if status looks  like
		"ignored (reached end-of-life)", this means that this given Ubuntu release already reached
		end-of-life so this CVE is ignored by Ubuntu. However, if there
		is extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package (inside the given release) is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The package version that contains the fix is also
		  alongwith the status.

@@

\textbf{released-esm:} The package (inside the given release) was vulnerable and
		an update has been already uploaded and published. However,
		this update is published in the Ubuntu ESM release only and not in LTS.
		The fixed version of such packages is appended by
		+esmN or /~esmN, indicating that this package version is available
		only via ESM.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.
\subsection{Image size Reduction process}
If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
image size reduction process is a good choice. In this process we reduce the number of packages
installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
out which packages we need for the pipeline to fucntion properly. Here, we used 
Reprozip~\cite{rampin2016reprozip}. It is a tool that
is used to make applications reproducible. It traces operating system calls used by the
application while execution and then based on that it recognizes binaries, files, environment variables,
and library dependencies that will be used by the application for future reexecution. If the OS is
Debian or RPM based, Reprozip also
uses available package manager to acquire a list of distribution packages from where these files come from.
So, we got a list of packages from Reprozip that are needed for the application execution. 
After that, we expanded this list by adding important and required packages that are essential
for the system to function and finally figured out all the dependencies of these packages using Debtree
~\cite{debtree}.
Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
finally deletes unnecessary packages.

\subsection{Update and Size Reduction Together}

Our final experiment involves combination of both update and size reduction process
to lessen the number of vulnerabilities.
So in this process we first update all the packages in the image and then deletes
the unnecessary packages. For this process we used the same two scripts that
we used for earlier experiments.

@@

In this section,
we first discuss the existing vulnerabilities in the images and compare
results of the three scanners. Then we discuss the effect of the update on the
existing vulnerabilities followed by the results of the image size reduction
process. Lastly, this section presents the combined effect of update and image size reduction on the
vulnerabilities. Here, we want to mention that after update and minification process we scanned
images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.

@@

Table~\ref{sing} shows the number of vulnerabilities present in Singularity images whereas 
Figure~\ref{fig:venn} illustrates the number of vulnerabilities in Docker images, which are detected by the three scanners. The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
Figure~\ref{sing}
\begin{table*}
\csvreader[%
 respect all,%
  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
      \begin{adjustbox}{max width=\textwidth},
  after reading=\end{adjustbox},
 tabular={c |c | c | c | c |c},
	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
 late after line= \\,
        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
]{results.csv}{}{\csvlinetotablerow}%
       \centering
	\caption{\label{table1}Existing number of Vulnerabilities}
\end{table*}
%\begin{comment}
%\begin{table}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c|c},
%	table head ={Image Tag} & {Image Name}\\\hline,
% late after line= \\,
%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{names.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{\label{table2}Image names}
%\end{table}
%\end{comment}
\begin{figure}[H]
        {\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/vennDiagram.pdf}}
        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
\end{figure}

@@

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. At the time of writing, these reasons include bugs in scanners,
some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
and how frequently they are updating their databases, etc.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them all.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.
Linux-kernel-headers are the headers files that only provide function names, its parameters, and its
return type.
The actual source code of these functions is present in the Linux kernel and is not inside the image.
So, vulnerability detection in header files
is irrelevant in this case.

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
affected by this CVE.

\textbf{CVEs with status as "Ignored (reached end-of-life)":}
Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
release so Clair Scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images still
Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.

@@

\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
		detected by Anchore due to the presence of epoch in the Procps package version.
		We reported this bug to the team through the slack channel.

\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

\textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
		For example CVE-2019-5094 vulnerability.

@@

\begin{figure*}[b]
        {\includegraphics[scale=1.5,width=\textwidth]
        {Figures/bargraph.png}}
        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
      \end{figure*}

\subsection{Effect Of Update}
%\begin{comment}
%The next experiment involves updating all these images and then rescanning them to see how the number of
%vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
%present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
%{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
%will find the package manager inside the image and then update the image according to the package manager it finds.
%\end{comment}

As the effect of update,
scanning results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date.
%\begin{comment}
%There are only two
%options, either you accept those vulnerabilities and use that image, or you discard that image.
%So one thing is clear here that even if we keep our images up to date there will be still some
%vulnerabilities that we have to face.
%\end{comment}
Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
the update of these images. 
%In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
In fact, this image combines original results of Figure~\ref{fig:graph1} with the results of update.
Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
significant number. Furthermore, a mild slope of vulnerabilities after the update shows that
there is a set of packages that contain vulnerabilities and have no fix yet. Also, these
vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
critical vulnerability are patched with high priority.
Besides that, it is also interesting to note that some images in the Figure~\ref{fig:graph2}
do not have update results. This is because some Linux distributions reached end-of-life and
are not getting updates anymore.

%After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
%Also, after the update, the number of vulnerabilities have a mild slope meaning that there
%are a fixed set of packages that contain vulnerabilities and have no fix yet.
%\begin{figure*}[h]
%        {\includegraphics[width=\textwidth]
%        {Figures/vulnwithupdate.pdf}}
%        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
%	after update of the images}
%      \end{figure*}

\begin{figure}[H]
        \fbox{{\includegraphics[scale=2.5,width=\columnwidth]
        {Figures/graphwithdeletedpackages.pdf}}}
	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
\end{figure}

@@

Our third experiment involves deleting unnecessary packages from the images.
We did this experiment only on five images because reduction process takes a
while. We selected these five images at random. We noticed that
after the size reduction process, the scanning results deviate a little from our initial belief.
At first, we thought that we will have notable effect of size reduction on
vulnerabilities. However, this is not the case always. The bar graph shown in
the Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
\textit{poldracklab/fmriprep:1.2.3} have insignificant effect of size reduction.
According to our analyzes here, this can be due to two reasons: \rom{1}) number
of unnecessary packages that we deleted and \rom{2}) type of packages that we deleted. In other
words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
In contrast, if the number of deleted packages are high, reduction
in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
reduced only by 4 and 17 respectively. Furthermore, this can be illustrated by Figure~\ref{deleted}.
Also, if we delete packages that contain a lot of vulnerabilites, it helps in reducing
vulnerabilities by a significant number. For instance, in case of our experiments
deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
%the number of vulnerabilities by a significant number. We started this experiment with
%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
%from 353 to 101.

@@

Our last experiment includes updating the image and then removing unnecessary packages from it.
Figure~\ref{fig:bargraph} displays the results. 
Our initial thought was that with the update and size reduction process together, we will be able to
reduce vulnerabilities even more. However
we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
many vulnerabilities they contained. To illustrate, \textit{bids/example} image in the Figure~\ref{fig:bargraph}
shows no effect of size reduction alongwith update. It has 181 vulnerabilities for both experiments 2 and 4.
Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
scanning results did not change.

@@

As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can reply upon for
scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
already reached end-of-life and are
no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
the pipeline to get Reprozip trace that can take upto several hours. Also, user should have proper knowledge
of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
branch of the program. So there should be some kind of coverage measurement.
